---
output: word_document
editor_options: 
  chunk_output_type: console
---
#7TotaldescriptivaClean5.Rmd
#install.packages("rmarkdown")
#library("rmarkdown")

READING CREDSCO.CSV. NOTE: Change the path of the file for the proper one in your computer. 

Remember that subfolders must be indicated by "/" and not by "\"

Here you can write the introduction of your report and include some text that will be transferred to the word file every time you re-run this Markdown

WARNING: data must have been properly declared before (factors, dates...)
```{r}
# dd <- read.table("D:/karina/docencia/areferenciesPPT/0DadesPractiques/CREDSCO/credscoCategoriques2.csv",header=T, sep=";", dec=",")
#dd<- read.csv("D:/karina/TFGs/GrauEstadistica/MarcPinar/data.csv", sep=";")

#dataset<-"platjaDaro"
#dataset<-"futbol"

#setwd("D:/karina/projectes/ON/a2020INSESSCOVIDisocial/18DadesTallers")
#dd<- read.table("2Formulari5TPlataDarov1.csv",header=T, sep=",", dec=".", na.strings="*");
#dataset<-"planta"

dataset<-"CREDSCO"



```

Set the folder where the word file is going to be generated
```{r}
library(readxl)
setwd("C:/Users/11ser/OneDrive/Escritorio/Coding/Uni/Quatri_2/Estadística/")
dd <- read_excel("C:/Users/11ser/OneDrive/Escritorio/Coding/Uni/Quatri_2/Estadística/database.xlsx")

```  

Check the type of the R object created for the dataset

```{r}            
class(dd)
```

without including the R instruction in the final document

```{r, echo=FALSE}            
class(dd)
```

Get dimensions of the dataset
```{r}
dim(dd)
n<-dim(dd)[1]
K<-dim(dd)[2]

n
K
```
Check the variables 

```{r}
names(dd)
```
Decide if you need to declare some more factor or date

```{r}
is_numeric_or_date <- function(X) {
  is.numeric(X) || inherits(X, "Date")
}

descriptiva <- function(X, nom) {
  # Check if X is a data frame and handle each column individually
  if (is.data.frame(X)) {
    for (col in names(X)) {
      print(paste("Analyzing column:", col))
      descriptiva(X[[col]], col)
    }
    return()  # Exit after processing all columns
  }
  
  if (!is_numeric_or_date(X)) { 
    frecs <- table(as.factor(X), useNA = "ifany")
    proportions <- frecs / length(X)
    # ojo, decidir si calcular porcentages con o sin missing values
    pie(frecs, cex = 0.6, main = paste("Pie of", nom))
    barplot(frecs, las = 3, cex.names = 0.7,ylim=c(0,600), main = paste("Barplot of", nom), col = rainbow(length(frecs)))
    print(paste("Number of modalities: ", length(frecs)))
    print("Frequency table")
    print(frecs)
    print("Relative frequency table (proportions)")
    print(proportions)
    print("Frequency table sorted")
    print(sort(frecs, decreasing = TRUE))
    print("Relative frequency table (proportions) sorted")
    print(sort(proportions, decreasing = TRUE))
  } else {
    if (inherits(X, "Date")) {
      print(summary(X))
      # Standard deviation for dates isn't typically useful, but if needed:
      # Convert to numeric first (e.g., number of days since origin)
      numeric_dates <- as.numeric(X)
      print(paste("sd: ", sd(numeric_dates, na.rm = TRUE)))
      hist(X, breaks = "weeks", main = paste("Histogram of", nom))
    } else {
      
      hist(X, ylim=c(0,250), main = paste("Histogram of", nom))
      boxplot(X, horizontal = TRUE, main = paste("Boxplot of", nom))
      print("Extended Summary Statistics")
      print(summary(X))
      print(paste("sd: ", sd(X, na.rm = TRUE)))
      print(paste("vc: ", sd(X, na.rm = TRUE) / mean(X, na.rm = TRUE)))
    }
  }
}



dataset<-dd
actives<-c(1:K)
colDate<-1
#if (dataset=="platjaDaro")
#  {dd[,colDate]<-as.Date(dd[, colDate], format="%d/%m/%y %h:%m:%s")
  # actives<-c(3:44)
 #  }

```


Basic descriptive analysis for numerical variables

(decide the maximum number of colors you can need in a graph based on your metadata file)
```{r, echo=FALSE}
listOfColors<-rainbow(39)

par(ask=TRUE)

for(k in actives){
  print(paste("variable ", k, ":", names(dd)[k] ))
  descriptiva(dd[,k], names(dd)[k])
}
par(ask=FALSE)

#per exportar figures d'R per programa
#dev.off()
#png(file=mypath,width = 950, height = 800, units = "px")
#dev.off()

```
